\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions

### 2021-08-27 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS_10pg.tex
updates

\begin{figure*}[ht!]
   \subfigure[]{\includegraphics[width=0.322\textwidth]{Case0_OmegaMarginals.png}}
   \hspace{\fill}
   \subfigure[]{\includegraphics[width=0.322\textwidth]{Case1_OmegaMarginals.png}}
   \hspace{\fill}
   \subfigure[]{\includegraphics[width=0.309\textwidth]{Case0Case1Combined_Gen4_OmegaMarginals.png}}
\caption{\small{For $i=1,\hdots,5$, the $\omega_{i}$ marginals (a) for Case I, and (b) for Case II, resulting from the IEEE 14 bus simulation described in Sec. \ref{subsec:NumSimIEEEBus}. (c) Comparison of the $\omega_{4}$ marginals for bus 6 in the nominal (Case I) and post-fault (Case II) scenarios.}}
\vspace*{-0.1in}
\label{fig:IEEE14omegamarginalsCase12}
\end{figure*}

\begin{figure}[t]
\centering
\includegraphics[width=0.95\linewidth]{ComputationalTimeSyntheticIEEE14busCase1and2combined.png}
\caption{\small{The computational time for propagating the transient joint state PDFs over $\mathbb{T}^{5}\times\mathbb{R}^{5}$ for the simulation set up in Sec. \ref{subsec:NumSimIEEEBus}.}}
\vspace*{-0.1in}
\label{fig:CompTimeIEEE14bus}
\end{figure}

>>>>

%\begin{figure*}[ht!]
%   \subfigure[]{\includegraphics[width=0.322\textwidth]{Case0_OmegaMarginals.png}}
%   \hspace{\fill}
%   \subfigure[]{\includegraphics[width=0.322\textwidth]{Case1_OmegaMarginals.png}}
%   \hspace{\fill}
%   \subfigure[]{\includegraphics[width=0.309\textwidth]{Case0Case1Combined_Gen4_OmegaMarginals.png}}
%\caption{\small{For $i=1,\hdots,5$, the $\omega_{i}$ marginals (a) for Case I, and (b) for Case II, resulting from the IEEE 14 bus simulation described in Sec. \ref{subsec:NumSimIEEEBus}. (c) Comparison of the $\omega_{4}$ marginals for bus 6 in the nominal (Case I) and post-fault (Case II) scenarios.}}
%\vspace*{-0.1in}
%\label{fig:IEEE14omegamarginalsCase12}
%\end{figure*}

\begin{figure}[ht!]
\includegraphics[width=0.95\linewidth]{Case0Case1Combined_Gen4_OmegaMarginals.png}
\caption{\small{Comparison of the $\omega_{4}$ marginals for bus 6 in the nominal (Case I) and post-fault (Case II) scenarios in the IEEE 14 bus simulation described in Sec. \ref{subsec:NumSimIEEEBus}.}}
\vspace*{-0.1in}
\label{fig:IEEE14omegamarginalsCase12}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics[width=0.9\linewidth]{ComputationalTimeSyntheticIEEE14busCase1and2combined.png}
\caption{\small{The computational time for propagating the transient joint state PDFs over $\mathbb{T}^{5}\times\mathbb{R}^{5}$ for the simulation set up in Sec. \ref{subsec:NumSimIEEEBus}.}}
\vspace*{-0.1in}
\label{fig:CompTimeIEEE14bus}
\end{figure}
